|

### 2023-03-10 paper/paper.Rmd
renamed files

@@

@@

@@

>>>>

```{r}
#| label: fig_field
#| fig.cap: "snapshots"
#| fig.width: 7
#| fig.height: 9
source(here("scripts", "01_fig_field.R"))
fig_field
```

Figure \ref{fig:fig_field} shows snapshots

```{r}
#| label: fig_crosby_curves
#| fig.cap: "crosby"
#| fig.width: 5
#| fig.height: 3
source(here("scripts", "02_fig_crosby_curves.R"))
fig_crosby_curves
```

Figure \ref{fig:fig_crosby_curves} shows Crosby throughout the play

@@

```{r}
#| label: fig_pos_curves
#| fig.cap: "STRAIN curves for different positions"
#| fig.width: 4.5
#| fig.height: 3
source(here("scripts", "03_fig_pos_curves.R"))
fig_pos_curves
```

Figure \ref{fig:fig_pos_curves} shows pos curves

@@

```{r}
#| label: fig_cor_pressure
#| fig.cap: "Cor with"
#| fig.width: 4
#| fig.height: 3
source(here("scripts", "04_fig_cor_pressure.R"))
fig_cor_pressure
```

Figure \ref{fig:fig_cor_pressure} shows cor with pressure

Fairly strong correlation (r = 0.6254943) between average STRAIN & hurries + sacks + hits per snaps

@@

```{r}
#| label: fig_stability
#| fig.cap: "Metric stability"
#| fig.width: 4
#| fig.height: 3
source(here("scripts", "05_fig_stability.R"))
fig_stability
```

0.8544865

Figure \ref{fig:fig_stability} shows

Average STRAIN across all frames played in first and last 4 weeks

Strong correlation shows great metric stability
